Quantifying Directionality and Innovation Output in Sweden's Transition to a Forest-Based Bioeconomy

### 2024-05-07 experiments/14-plots.qmd
add vision_counts.pdf plot

```{r}
#| label: fig-n-innovation

innovation_plot <- plot_bioeconomy_stats(bioeconomy_share, "ma5_n_innovation", "Total SWINNO")
```

@@

>>>>

```{r}
#| label: fig-n-innovation
innovation_plot <- plot_bioeconomy_stats(bioeconomy_share, "ma5_n_innovation", "Total SWINNO")
```

@@

## Bioeconomy Visions Plot

```{r}
visions <- import(here("data/modified/count_certain_visions.csv"))

vision_summary <- visions |>
    group_by(bioeconomy_vision) |>
    summarize(total_count = sum(count))

visions <- merge(visions, vision_summary, by = "bioeconomy_vision")

```

```{r}
batlow_discrete <- paletteer::paletteer_c("scico::batlowW", n = 5)
```

```{r}
#| label: fig-vision-count
vision_count_plot <- ggplot(visions, aes(x = year, y = count, color = bioeconomy_vision, fill = bioeconomy_vision)) +
    geom_col(alpha = 0.9, linewidth = 0.75) +
    facet_wrap(~bioeconomy_vision) +
    scale_color_manual(values = batlow_discrete) +
    scale_fill_manual(values = batlow_discrete) +
    theme_custom() +
    theme(legend.position = "none") +
    scale_y_continuous(breaks = seq(0, max(visions$count), by = 2), expand = c(0, 0)) +
    xlab("Year") +
    ylab("Innovation Count") +
    geom_text(
        data = vision_summary, aes(label = paste("Total:", total_count), x = Inf, y = Inf),
        position = position_nudge(y = 0), hjust = 1, vjust = 1.3, size = 3.5
    )

ggsave(here("results/figures/vision_count.pdf"), vision_count_plot)
```
